PMC Survey Data Analysis

### 2021-08-05 analysis.Rmd
jif

library("wordcloud")
library("RColorBrewer")
library("wordcloud")

@@

>>>>

library("wordcloud")
library("RColorBrewer")
library("wordcloud2")

@@

## Journal rank

```{r,journal rank}

jmetrics <- read.table("scimagojr_2020.csv",sep=";",header=TRUE,dec = ",")
jmetrics$Title <- toupper(jmetrics$Title)
head(jmetrics)
dim(jmetrics)

nlmcat <- readLines("nlmcatalog_result.txt")
journaltitle <- nlmcat[grep("Title\\(s\\):",nlmcat)]
journaltitle <- gsub("Title\\(s\\): ","",journaltitle)
journaltitle <- gsub("\\.$","",journaltitle)
journaltitle <- toupper(journaltitle) 
head(journaltitle)
head(nlmcat)
journalabbrev <- nlmcat[grep("Title Abbreviation:",nlmcat)]
journalabbrev <- sapply(strsplit(journalabbrev,":"),"[[",2)
journalabbrev <- gsub(" $","",journalabbrev)
journalabbrev <- gsub("^ ","",journalabbrev)
head(journalabbrev)
jdf <- data.frame(journalabbrev,journaltitle)
head(jdf)

mjdf <- merge(jdf,jmetrics,by.x="journaltitle",by.y="Title")
head(mjdf)
dim(mjdf)

```
journalabbrev <- medline[grep("Title(s):",medline)]

jdf <- data.frame(journaltitle,journalabbrev)

m <- merge(jmetrics,jdf,by.x="Title",by.y="journaltitle")
dim(m)
mm <- m[,c("journalabbrev","SJR")]
dim(mm)

dim(x)
xm <- merge(x,mm,by.x="Journal",by.y="journalabbrev")
dim(xm)
tail(xm)

dim(x)
length(which(x$Journal %in% mm$journalabbrev))

x[which(! x$Journal %in% mm$journalabbrev),"Journal"]

mm$journalabbrev
head(x$Journal)
